BDP draft paper

### 2016-08-08 final_paper/draft.Rmd
test

### Analysis of Day
```{r, echo=FALSE, eval = FALSE}
stop_day <- stop_by %>%
  ggvis(x = ~Day, fill = ~Race) %>%
  layer_bars() %>%
  add_tooltip(function(stop_by) stop_by$Race)+
  labs(title = "Counts of people recorded in every day in a week")
stop_day
```

@@

>>>>

### Analysis of Day
```{r, echo=FALSE, eval = FALSE}
stop_day <- stop_by %>%
  ggvis(x = ~Day, fill = ~Race) %>%
  layer_bars() %>%
  add_tooltip(function(stop_by) stop_by$Race) 
  labs(title = "Counts of people recorded in every day in a week")
stop_day
```

@@

```{r}

  theme(axis.line = element_line(size=1, colour = "black"), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        panel.border = element_blank(), 
        panel.background = element_blank())

  theme(plot.title=element_text(family="xkcd-Regular"), 
        text=element_text(family="xkcd-Regular"), 
        axis.text.x=element_text(colour="black", size = 10), 
        axis.text.y=element_text(colour="black", size = 10))

p1 <- ggplot(stop_by)+
  geom_bar(aes(x=Race),
           fill = c("#FFCC00","#000000","#330099","#66FFCC","#FFFFFF"))+
  labs(title = "Stop data by race",
       x = "Race",
       y = "Counts")

p2 <- ggplot(race)+
  geom_bar(aes(x=Description, 
               y=Counts),
           stat = "identity", 
           fill = c("#FFCC00","#000000","#330099","#66FFCC","#FFFFFF"))+
  labs(title = "Demographic race data",
       x = "Race",
       y = "Counts")

ggplot(mtcars, aes(factor(cyl))) + 
          geom_bar(aes(y = (..count..)/sum(..count..))) + 
          scale_y_continuous(labels=percent)

ggplot(pop)+
  geom_bar(aes(x=Race,
               y=(stop/census)), 
           stat = "identity",
           fill = c("#FFCC00","#000000","#330099","#66FFCC","#FFFFFF"))+
  geom_text(aes(x = Race, 
                y = (stop/census), 
                label = paste0((stop/census),"%")), 
            size=3)+
  scale_y_continuous(labels=percent)+
  labs(title = "The percentage of being stopped by police",
       x = "Race",
       y = "Percentage")

```{r}
############################## stop data ############################## 
stop_by <- read_csv("cleaned_stop_data.csv")

stop_by$CarSearch <- stop_by$CarSearch %>% 
  str_replace("S", "Search") %>% 
  str_replace("N", "No Search")
```
